---
title: "Eyetracking Task"
output: html_document
---

```{r}

pacman::p_load(tidyverse, lmerTest)
```

## Load data 
The data has been cleaned a bit already. If you need the raw data for your analysis, let me know. 
```{r}
#Set your WD here:
setwd("C:/Users/Mikkel/Documents/UNI/masters/HCI/Eye tracking task/Eye tracking task")
df <- read.csv("clean_data.csv")

df$website <- as.factor(df$website)
df$event <- as.factor(df$event)
df$name <- as.factor(df$name)
```


## The experiment set-up 
The data contains data from 10 participants. They were asked to order 2 cinema tickets for the movie Parasite on Friday evening on both the Cinemax and the NFbio websites. During the experiment, the participants eye movements, pupil diameter and mouse movements were recorded. 


## Variable key 
#### DEMOGRAPHICS
- name: the name of the participant
- age: its age
- order_tickets_online: how often does the participant order cinema tickets online (3 levels: never, rarely, often)
- cinemaxx_1st: wether they started with the cinemaxx or nfbio website (binary: 1 -> cinemaxx, 0 -> nfbio)
- session: which session the datapoint belongs to (2 levels)
- website: which website was being explored (2 categories: cinemaxx, nfbio)

#### TIME VARIABLES
- timestep: the eyetracker saves series of frames, this indicates the number of the frame starting from the beginning of the capture (by session, within participant)
- time: time from beginning of the experiment by participant and session (in ms)
- tp: time from beginning of the experiment at the next step (basically, t+1, in ms)
- timegap: amount of time between this time step and the previous one (t - (t-1), in ms)

#### GAZE VARIABLES
- x: horizontal position of the gaze on the screen (in pixels)
- y: vertical position of the gaze on the screen (in pixels)
- xp: horizontal position of the gaze on the screen at time t+1 (in pixels)
- yp: vertical position of the gaze on the screen at time t+1 (in pixels)
- velocity: the velocity of eye movement between t and t+1 (in pxl/ms)

#### FIXATION/SACCADE VARIABLES
- event: wether the movement has been categorised as a saccade or a fixation based on velocity at this timestep (2 categories: fixation, saccade)
- event_n: list the events in the order they appeared (by session within participant) /!\ CAREFUL /!\, lists of saccades and fixations are independent but in the same column!
- event_d: the duration of the event (by event_n) (in ms)
- center_mean: mean velocity of the current participant for the corresponding type of event

#### OTHER VARIABLES
- pdl: pupil dilation of the left eye (in mm)
- pdr: pupil dilation of the right eye (in mm)
- mouse_x: mouse horizontal position at the current timestep (in pixels)
- mouse_y: mouse vertical position at the current timestep (in pixels)


#### DATA PROCESSING
Although the data has been cleaned, you might need to transform some variables depending on the ideas you have.  

For example, if you are interested in synchronicity between gaze velocity and mouse velocity, you will need to calculate the velocity of mouse movements. (Not that you should be interested in that. Really.)
```{r}

## CLEANING AND PROCESSING HERE - if needed ##
summary(df$website)
summary(df$name)

### BAYESIAN NEEDS 0's AND 1'S ###

df <- df %>%
  mutate(event_num = factor(ifelse(event == "fixation", 1, 0)),
         website_num = ifelse(website == "nfbio", 1, 0),
         velocity_log = velocity + 0.00001)

df_mean_vel = df %>%
  select(name, event, website, center_mean) %>%
  group_by(name, event, website) %>%
  summarize(mean_vel = mean(center_mean), n = n())

df_outlier = df %>%
  filter(event_d < 20000)

df_time = df %>% 
  group_by(name, website_num) %>%
  summarise(time_max = max(timestep)) %>%
  glimpse()

df_cor = df %>%
  select(!c(name, age, order_tickets_online, website, event, event_num))

library(pacman)
p_load(corrplot)

M = cor(df_cor)

corrplot(M, method = "circle", type = "upper")
```

INITIAL TAKE AWAY:

Sfbio is much more simple, and present information in more clear way. It is therefore deemed plausible that (1) there will be fewer saccades relative to fixations and as a consequence of this, the mean velocity will be lower for sfbio. 


#### An Example
Here is an example of a model you could build with the given data: 
```{r}
# Here is a prelimniary model:
# 1. What is it asking?
# 2. How would you interpret these results?
# 3. How would you improve it?
m1 <- glmer(event ~ website + (1|name) + (1|cinemaxx_1st), df, family = binomial)
summary(m1)
```

```{r}
m2 <- glmer(website_num ~ event_num + (1|name) + (1|cinemaxx_1st), df)
summary(m2)


```

```{r}
m3 <- glmer(event ~ order_tickets_online + (1|name), df, family = binomial)
summary(m3)
```


#### GO WILD

Using eye tracking, what are good indices of usability?  
For inspiration, you can refer to the following article:  
https://openaccess.city.ac.uk/id/eprint/3917/1/

Make predictions and test them out on this data set.Fancy plots are welcome   

Here are some suggestions:  
1) look at number of fixations/saccades
2) look at durations of fixations/saccades
3) the ratio between fixation and saccades
4) entropy/variability of saccades (?)
5) other? 

```{r}
#Test your hypothesis here :D 
```


Some alternative Bayesian Approach:

First predicting event by website

```{r}
library(pacman)
p_load(tidyverse, brms, broom)

get_prior(data = df,
          family = binomial,
          website ~ event_num + (1|name) + (1|cinemaxx_1st))

priors = c(prior(normal(0,2), class = b),
           prior(normal(0, 10), class = Intercept),
           prior(normal(0,10), class = sd, group = name),
           prior(normal(0,10), class = sd, group = cinemaxx_1st))

fit = brm(data = df,
          family = bernoulli(link = "logit"), #alternatively this could be binomial, but bernoulli is more fitting
          website ~ event_num + (1|name) + (1|cinemaxx_1st),
          prior = priors,
          seed = 42,
          chains = 3,
          iter = 1000)


### NOTE: Since we are only dealing with 0's and 1's, 
## to use the bernoulli distribution.
```

```{r}
summary(fit)
pp_check(fit)
plot(fit)

summary(df$event_num)

exp(fixef(fit)[,-2]) #model estimates that the 

```

```{r}
get_prior(data = df,
          family = lognormal(),
          velocity ~ website + (1|name))

priors = c(prior(normal(0,2), class = b),
           prior(normal(0, 10), class = Intercept),
           prior(normal(0,10), class = sd, group = name),
           prior(normal(0.5, 0.5), class = sigma))

fit2 = brm(data = df,
           family = lognormal(),
           velocity_log ~ website + (1|name),
           prior = priors,
           seed = 42)

summary(fit2)
pp_check(fit2)
plot(fit2)
```

```{r}

## Are event durations different for the two websites? Nope!

ggplot(df %>% filter(event == "fixation"), aes(event, event_d, color = website)) +
  geom_point()+
  geom_violin()

#What about saccades? Nope!

ggplot(df %>% filter(event == "saccade"), aes(event, event_d, color = website)) +
  geom_point()+
  geom_violin()

# Are more experienced users good at staying on target? Not really.

ggplot(df%>%filter(event == "saccade"), aes(order_tickets_online, event_d, color = website)) +
  geom_point() +
  geom_violin()

#People might be a bit better at staying on target on nfbio? But again, effect is driven by a couple of datapoints.

ggplot(df_outlier%>%filter(event == "fixation"), aes(order_tickets_online, event_d, color = website)) +
  geom_point() +
  geom_violin()

# Where do people look on the screen?

fix = ggplot(df%>% filter(event == "fixation"), aes(x, y, color = website)) +
  geom_point(alpha = 0.01) +
  geom_density2d() + 
  labs(title = "Fixations")

mouse = ggplot(df, aes(mouse_x, mouse_y, color = website)) +
  geom_point(alpha = 0.01) +
  geom_density2d() +
  labs(title = "Mouse position")

p_load(cowplot)

plot_grid(fix, mouse, nrow = 2)

```

